---
title: "ANOVA_stimStrength-att"
author: "Karen Tian"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, echo = FALSE, include=FALSE}
# include prevents code and results from being displayed
# echo prevents code 
suppressPackageStartupMessages(library(tidyverse))
library(ez)
library(foreach)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(lsr)
library(report)
library(rempsyc) # for t-tests in nice tables
library(broom)
library(huxtable) # another table making package
knitr::opts_chunk$set(echo = TRUE)

#### set path #### 
# wd  <- '/Users/kantian/Dropbox/github/TWCF_FOHO/twcf_expt1_stats_BU/'
# setwd(wd)

#### anova setup #### 
options(contrasts=c("contr.sum","contr.poly"))

#### load AUC data #### 
analysisName = "twcf_expts1-4_byContrast";
dataName <- sprintf("../data/%s.csv",analysisName)
data <- read_csv(dataName)

#### Change to categorical vars ####
data$expt <- as.factor(data$expt)
data$site <- as.factor(data$site)
data$subjectID <- as.factor(data$subjectID)
data$attention <- as.factor(data$attention)
data$stimStrength <- as.factor(data$stimStrength)

### Plotting setup #### 
colors = c("#F8A299","#CCCCCC","#98E6A1")
attComparison <- list( c("1","3"), c("1","2"), c("2","3") )

significance <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, Inf),
symbols = c("****", "***", "**", "*", "ns"))
```

Performance  
 • [all expts](#Performance-as-a-function-of-stimulus-strength-(all-expts))  
Overall visibility  
Task-relevant feature visibility 
 
## Performance as a function of stimulus strength (all expts)
Remove contrast 0 for Expt 3 for balanced design
```{r anova-expt1-4, echo = FALSE}
dS <- data %>% filter(stimStrength!=0) 
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site,stimType,taskType),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Performance by stimulus strength (expts 1-4) ANOVA")

## Performance by stimulus strength
d <- dS %>% group_by(stimStrength) %>%
  summarise(mean=mean(correctDis), sd=sd(correctDis), n=n_distinct(subjectID)) %>% mutate(se = sd / sqrt(n),
         ci.lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         ci.upper = mean + qt(1 - (0.05 / 2), n - 1) * se)
knitr::kable(d, digits=3, caption="Performance by stimulus strength (expts 1-4) summary stats")
```

## Performance across successive stim strenghts
```{r anova-expt1-4-successive, echo = FALSE}
dS <- data %>% filter(stimStrength==1 | stimStrength==2) 
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Performance between stimulus strengths 1 vs 2 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==2 | stimStrength==3) 
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Performance between stimulus strengths 2 vs 3 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==3 | stimStrength==4) 
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Performance between stimulus strengths 3 vs 4 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==4 | stimStrength==5) 
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Performance between stimulus strengths 4 vs 5 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==5 | stimStrength==6) 
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Performance between stimulus strengths 5 vs 6 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==6 | stimStrength==7) 
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Performance between stimulus strengths 6 vs 7 (expts 1-4) ANOVA")
```

## Performance as a function of stimulus strength (expt 1)
```{r anova-expt1, echo = TRUE}
dS <- data %>% filter(expt==1)
m_anova = ezANOVA(
  data = dS,
  dv = .(correctDis),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
options(scipen = 0)
knitr::kable(m_anova$ANOVA, digits=3, escape = FALSE)

## Performance by stimulus strength
d <- dS %>% group_by(stimStrength) %>%
  summarise(mean=mean(correctDis), sd=sd(correctDis), n=n_distinct(subjectID)) %>% mutate(se = sd / sqrt(n),
         ci.lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         ci.upper = mean + qt(1 - (0.05 / 2), n - 1) * se)
knitr::kable(d, digits=3, caption="Performance by stimulus strength (expt 1)")
```

## Overall visibility as a function of stimulus strength
All expts, remove contrast 0 for Expt 3 for balanced design
```{r anova-expt1-4-ov, echo = TRUE}
dS <- data %>% filter(stimStrength!=0) 
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeen),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site,stimType,taskType),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Overall visibility by stimulus strength (expts 1-4) ANOVA")

## Overall visibility by stimulus strength
d <- dS %>% group_by(stimStrength) %>%
  summarise(mean=mean(pSeen), sd=sd(pSeen), n=n_distinct(subjectID)) %>% mutate(se = sd / sqrt(n),
         ci.lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         ci.upper = mean + qt(1 - (0.05 / 2), n - 1) * se)
knitr::kable(d, digits=3, caption="Overall visibility by stimulus strength (expts 1-4) summary stats")
```

## Overall visibility across successive stim strengths
```{r anova-expt1-4-ov-successive, echo = FALSE}
dS <- data %>% filter(stimStrength==1 | stimStrength==2) 
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeen),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Overall visibility between stimulus strengths 1 vs 2 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==2 | stimStrength==3) 
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeen),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Overall visibility between stimulus strengths 2 vs 3 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==3 | stimStrength==4) 
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeen),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Overall visibility between stimulus strengths 3 vs 4 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==4 | stimStrength==5) 
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeen),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Overall visibility between stimulus strengths 4 vs 5 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==5 | stimStrength==6) 
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeen),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Overall visibility between stimulus strengths 5 vs 6 (expts 1-4) ANOVA")

dS <- data %>% filter(stimStrength==6 | stimStrength==7) 
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeen),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Overall visibility between stimulus strengths 6 vs 7 (expts 1-4) ANOVA")
```

## Task-relevant feature visibility as a function of stimulus strength
Expts 134 (1,2,4), remove contrast 0 for Expt 3 for balanced design
```{r anova-expt1-4-fv, echo = TRUE}
dS <- data %>% filter(stimStrength!=0) %>% filter(expt!=2)
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeenFeature),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Task-relevant feature visibility by stimulus strength (3 expts) ANOVA")

## Task-relevant feature visibility by stimulus strength
d <- dS %>% group_by(stimStrength) %>%
  summarise(mean=mean(pSeenFeature), sd=sd(pSeenFeature), n=n_distinct(subjectID)) %>% mutate(se = sd / sqrt(n),
         ci.lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         ci.upper = mean + qt(1 - (0.05 / 2), n - 1) * se)
knitr::kable(d, digits=3, caption="Task-relevant feature visibility by stimulus strength (expts 1-4) summary stats")
```

## Feature visibility across successive stim strenghts
```{r anova-expt1-3-fv-successive, echo = FALSE}
dS <- data %>% filter(stimStrength==1 | stimStrength==2) %>% filter(expt!=2)
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeenFeature),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Feature visibility between stimulus strengths 1 vs 2 (expts 1-3) ANOVA")

dS <- data %>% filter(stimStrength==2 | stimStrength==3) %>% filter(expt!=2)
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeenFeature),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Feature visibility between stimulus strengths 2 vs 3 (expts 1-3) ANOVA")

dS <- data %>% filter(stimStrength==3 | stimStrength==4) %>% filter(expt!=2)
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeenFeature),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Feature visibility between stimulus strengths 3 vs 4 (expts 1-3) ANOVA")

dS <- data %>% filter(stimStrength==4 | stimStrength==5) %>% filter(expt!=2)
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeenFeature),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Feature visibility between stimulus strengths 4 vs 5 (expts 1-3) ANOVA")

dS <- data %>% filter(stimStrength==5 | stimStrength==6) %>% filter(expt!=2)
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeenFeature),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Feature visibility between stimulus strengths 5 vs 6 (expts 1-3) ANOVA")

dS <- data %>% filter(stimStrength==6 | stimStrength==7) %>% filter(expt!=2)
m_anova = ezANOVA(
  data = dS,
  dv = .(pSeenFeature),
  wid = .(subjectID),
  within = .(attention,stimStrength),
  between = .(site),
  detailed = TRUE,
  )
knitr::kable(m_anova, digits=3, caption="Feature visibility between stimulus strengths 6 vs 7 (expts 1-3) ANOVA")
```