---
title: "TWCF_LMM"
output: github_document
date: "2024-04-23"
---

```{r setup, include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(ez)
library(foreach)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(lsr)
library(report)
library(rempsyc) # for t-tests in nice tables
library(lme4)
library(lmerTest)
library(sjstats)

library(tidyverse) # needed for data manipulation.
library(RColorBrewer) # needed for some extra colours in one of the graphs
library(RRPP)

knitr::opts_chunk$set(echo = TRUE)

#### set path #### 
wd  <- getwd()

#### anova setup #### 
options(contrasts=c("contr.sum","contr.poly"))
```

```{r loaddata, include=FALSE}
#### load twcf single trial data #### 
analysisName = "Expts1-4_singleTrial";
dataName <- sprintf("%s/%s.csv",wd,analysisName)
data <- read_csv(dataName)

#### Change to factors ####
data$expt <- as.factor(data$expt)
data$subjectID = as.factor(data$subjectID)
data$site <- as.factor(data$site)
data$cueValidity <- as.factor(data$cueValidity)

# data$seen <- as.factor(data$seen)
# data$correct <- as.factor(data$correct)
```

- Use Generalized Linear Models (GLM) when residuals are not normally distributed
- We use a link function to do a nonlinear transform in relating predictors to prediction. A logistic link function produces binary outcomes, like in our tilt discrimination task. 

- Fixed effects don't vary within a cluster 
--- No assumed relationship within the levels (like gender)

- Random effects are observed
--- Random effects are assumed to have an influence on the dependent variable 
--- Random effects are indicated by (|)

- (1|subjectID) notation means: Intercepts can freely vary by subject but not the slopes
--- De-means within levels

```{r glm}
model_full <- glmer(formula = ratingDis ~ 1 + cueValidity * stimStrengthID_postcue + rand + stimStrengthID_max + (1|expt) + (1|subjectID) + (1|site), 
               data = data, family=binomial, nAGQ=0) 
summary(model_full)
performance::icc(model_full)

model_reduced <- glmer(formula = ratingDis ~ 1 + cueValidity + (1|expt) + (1|subjectID), 
               data = data, family=binomial, nAGQ=0) 
summary(model_reduced)
performance::icc(model_reduced)

model_reduced2 <- glmer(formula = ratingDis ~ 1 + cueValidity * stimStrengthID_postcue + stimStrengthID_max + (1|expt) + (1|subjectID) + (1|site),
               data = data, family=binomial, nAGQ=0) 

model_reduced3 <- glmer(formula = ratingDis ~ 1 + cueValidity * stimStrengthID_postcue + (1|expt) + (1|subjectID) + (1|site),
               data = data, family=binomial, nAGQ=0) 

# Model comparison 
# Is there merit in dropping a random effect? 
# model.comparison(model_full,model_reduced)
anova(model_full,model_reduced,"chisq")

anova(model_full,model_reduced2,"chisq")

anova(model_reduced2,model_reduced3,"chisq")

# What is nAGQ

# Plot 
# ggplot(fortify(model), aes(contrast, seen, color=exposure)) +
#   stat_summary(fun.data=mean_se, geom="pointrange") +
#   stat_summary(aes(y=.fitted), fun.y=mean, geom="line")
```
